Why a digital tax may be the only sustainable solution

### 2019-07-28 writing/shortNote/main.tex
New shortnote, with pictures. Please read whatsapp.

Each buyer has an individual demand curve that is negatively sloped, meaning
that the more expensive the product, the less the buyer purchases. Buyers also
always buy the from the cheapest available seller.

@@

\section{Results}
We can see in Figure [blank] that as $\lambda$ gets closer to 0, the more fit
company is able to sell to more buyers, and eventually become a dominant
market force. [add actual numbers here.] This is despite only a 1\% lower
cost-per-unit.

When $\lambda$ is present but not too large, we have healthy competition
without seeing competitors being run out of business.

@@

At MIT, we are currently developing a new form of taxation that leverages
benefits of digital market place with this mechanism. We hope to still capture
all of the benefits of low transaction costs, including increased trade and
fairness, while at the same time reducing the ability and incentive for sellers
with transaction costs close to 0.

>>>>

Each buyer has an individual, linear demand curve that is negatively sloped,
meaning that the more expensive the product, the less the buyer purchases.
Buyers also always buy the from the cheapest available seller.

@@

\section{Results}
We can see in Figure \ref{fig:no_tax}, where $\lambda=0$ and there is no
transaction cost, that Firm 1 is able to make 33\% more profit despite only a
1\% lower cost-per-unit. But in Figure \ref{fig:no_tax}, where there is a
significant transaction cost of $\lambda = .4$, the difference in profits
is much closer, with Firm 1 only earning 8\% more than firm 2, with the same
1\% difference in costs. This decrease in monopolization comes at a great cost
though, as both firm's profit in the first scenario is significantly higher
than in the second.

\begin{figure}[!htb]
	\centering
	\includegraphics[width=\textwidth/2]{no_tax.png}
	\caption{The trade-offs of the transaction costs are demonstrated.
		This figure depicts an economy where the is no distance-based tax. In the economy, the profits of both firms are high, but one firm has 33\% larger profits because of a slight advantage in having 1\% cheaper unit costs.}
	\label{fig:no_tax}
\end{figure}

\begin{figure}[!htb]
	\centering
	\includegraphics[width=\textwidth/2]{lambda=4Over10.png}
	\caption{
		In contrast to Figure \ref{fig:no_tax}, this figure depicts an economy with a significant transaction cost. The profits for both firms are significantly lower, but also are much closer, with Firm 1 earning 8\% more profit, as opposed to 33\% in the previous figure.}
	\label{fig:lambda=.4}
\end{figure}

@@

At MIT, we are currently developing a new form of taxation that leverages
benefits of digital market place with this mechanism. We hope to still capture
all of the benefits of low transaction costs, including increased trade,
profit, and  fairness, while at the same time reducing the ability and
incentive for sellers to monopolize.
